Final Paper

### 2016-08-08 paper/paper.Rmd
merging

However, we also wanted to see these words plotted by their valence score versus average star rating to visualize the actual trend between sentiment and rating, rather than just viewing what percentage of words lied above the mean rating.
```{r trend, echo = FALSE, message = F, fig.align = "center"}
summaries %>% 
  arrange(desc(reviews)) %>% 
  ggplot(aes(score, average_star)) +
  geom_point(aes(size = reviews)) +
  geom_text(aes(label = word, family = "Times New Roman"),
            vjust = 1, hjust = 1, check_overlap = TRUE) +
  geom_smooth(method = "lm", se = FALSE) +
  xlab("Valence Score") +
  ylab("Average Yelp Stars") +
  labs(title = "Average Yelp Star Rating vs. Valence Score") +
  scale_x_continuous(limits = c(-5,6), breaks = seq(-5, 5, 2)) +
  scale_y_continuous(limits = c(1, 5), breaks = seq(1, 5, 1)) +
  expand_limits(x = -6) +
  theme(text = element_text(family = "Times New Roman"))
```

@@

Lastly, we wanted to see what the mean rating was for each AFINN score since that would clearly indicate a correlation.

@@

As expected, higher AFINN scores did in fact result in higher mean business ratings.

>>>>

However, we also wanted to see these words plotted by their valence score versus average star rating to visualize the actual trend between sentiment and rating, rather than just viewing what percentage of words lied above the mean rating.

```{r trend, echo = FALSE, message = F, fig.align = "center"}
summaries %>% 
  arrange(desc(reviews)) %>% 
  ggplot(aes(score, average_star)) +
  geom_point(aes(size = reviews)) +
  geom_text(aes(label = word, family = "Times New Roman"),
            vjust = 1, hjust = 1, check_overlap = TRUE) +
  geom_smooth(method = "lm", se = FALSE) +
  xlab("Valence Score") +
  ylab("Average Yelp Stars") +
  labs(title = "Average Yelp Star Rating vs. Valence Score") +
  scale_x_continuous(limits = c(-5,6), breaks = seq(-5, 5, 2)) +
  scale_y_continuous(limits = c(1, 5), breaks = seq(1, 5, 1)) +
  expand_limits(x = -6) +
  theme(text = element_text(family = "Times New Roman"))
```

@@

Lastly, we wanted to see what the mean rating was for each AFINN score since that would clearly indicate a correlation. We expected that lower scores would have lower mean business ratings, and higher scores would have higher mean ratings.

@@

As expected, higher AFINN scores did in fact result in higher mean business ratings. Interestingly, words with a -5 AFINN rating had a higher rating than words with a -4 and -3 AFINN rating. We're not exactly sure what would've caused this, but it seems like an interesting thing to explore for further research.
